### 2019-12-05 thesis.tex
Now it's the final version! =D

  particles, named \emph{electrostatic bremsstrahlung}. In the present study

@@

  and in it we compare the results of numerical integration of the rigorous

@@

  (numerical integration), the system seems to arrive to a new quasi-steady

@@

In the end, we have four appendices. \Cref{appA} depicts an improved
approximation for the second order susceptibility of the electrostatic
bremsstrahlung for Langmuir waves. In \Cref{appB} we discuss the
similarities of the asymptotic equilibrium state of the Langmuir waves
spectrum, considering a combination of an inverse power-law Kappa
distribution and a Maxwellian distribution, in the presence and the
absence of the electrostatic bremsstrahlung effect. The discussion in
\Cref{appB} is related to the article appended in \Cref{appC}, which
is parallel research and is only slightly connected to the main subject
of this work. \Cref{master} shows the paper that summarizes the results
of my Master’s dissertation, which may be considered the starting point
of this doctoral research. % \Cref{appE} explores relevant aspects of
% current solar physics research and how they are connected to this work.
% It was written to be more like a light, informative reading, than a
% deep academic digression.

@@

The following paper is fairly self-sustained regarding the theory and
methods applied. All important equations are there, including their
normalized form and the normalization constants. 
% Any doubt regarding the origin of the new equations is filled by \Cref{noneigenmode}.

\includepdf[pages=2-6]{Tigik2016b.pdf}
\section{Generation of suprathermal electrons by collective processes
  in collisional plasmas}
\label{sec:gen-supr}
For the analysis of the electrostatic bremsstrahlung, the simple integration
of Eqs. \eqref{PkL} and \eqref{PkS}
was not very clarifying since we did not have any equivalent effect for
comparison. So we had to perform the time evolution of the system and analyze
the outcome. However, in order to put in evidence the action of the new effect,
is useful to start with the simplest possible situation. Therefore, instead of
using the complete set of nonlinear weak turbulence equations given by
Eqs. \eqref{L-gen} and \eqref{S-gen}, we restrict our analysis to the
quasilinear formalism, which includes single particle spontaneous emission
and wave-particle induced emission, and add the collisional damping and
electrostatic bremsstrahlung effects. The particle kinetic equation is
given by the usual quasilinear equation, where we included the Landau
collision integral (the same used in \cite{Tigik2016a}). After a long
evolution period, the system reaches a steady state where the electron
velocity distribution strongly resembles a core-halo distribution. An
interesting and surprising detail is that this suprathermal electron
population grows even in the presence of binary collisions. In the next
two subsections we provide some helpful information regarding the equations
and methods employed in \cite{Tigik2017a}.

@@

\subsection{Dimensionless equations}
In order to simplify the numerical analysis, it is convenient to write
the equations in terms of dimensionless variables. Thus, let us start
by some important definitions
\begin{align*}
  z\equiv \frac{\omega}{\omega_{pe}},
  & \quad \tau\equiv \omega_{pe}t, \quad
    {\bf q}\equiv \frac{{\bf k}v_e}{\omega_{pe}}, \quad
    {\bf u}\equiv \frac{\bf v}{v_e},\\
  \mu_{\bf q}^L
  = 1,&\quad\mu_{\bf q}^S = \frac{q^3}{2^{3/2}}
	\,\sqrt{\frac{m_e}{m_i}}\;\biggl(1+\frac{3T_i}{T_e}\biggr)^{1/2},
\end{align*}
\begin{align*}
  \Phi_a({\bf u})=  v_e^3 F_a({\bf u}),& \quad
    \calE_{\bf q}^{\sigma\alpha}= \frac{(2\pi)^2 g}{m_ev_e^2}
    \frac{I_{\bf k}^{\sigma\alpha}}{\mu_{\bf k}^\alpha},\quad
    P_{\bf k}^\alpha=\frac{m_ev_e^2}{(2\pi)^2g}\omega_{pe}P_{\bf q}^\alpha,\\
\end{align*}
where $g=1/[2^{3/2}\,(4\pi)^2\,\hat{n}\,\lambda_{De}^3]$ is the
plasma parameter, $\lambda_{De}=T_e/(4\pi\hat{n}e^2)=v_e^2/(2\omega_{pe}^2)$,
$v_e=(2T_e/m_e)^{1/2}$ is the electron thermal velocity and $T_e$ is the
electron temperature.

@@

@@

\chapter{Extra publication}
\label{appC}
This publication is mainly related with the results presented in
Ref. \cite{Tigik2017a}.
We can say that most of the ideas about the physical processes occurring
in \cite{Tigik2017a}, regarding the formation of the core-halo velocity
distribution and the fact that the electrostatic bremsstrahlung could be
the underlying process behind the ubiquity of such velocity distribution
in the space environment, came from the analysis of the results presented
in \cite{Tigik2017b}.

@@

\chapter{Two-dimensional time evolution of beam-plasma
  instability in the presence of binary collisions}
\label{master}
The paper included in this appendix is the complete text of Ref.
\cite{Tigik2016a}, which summarizes the outcomes of the Master's
dissertation \cite{Tigik2015} that led to the current doctoral
research. This text was included here with the intention to give
the reader a complete view of the work developed during my graduate
studies.

>>>>

  particles, named \emph{electrostatic bremsstrahlung}. In the present study,

@@

  and in it, we compare the results of numerical integration of the rigorous

@@

  (numerical integration), the system seems to arrive at a new quasi-steady

@@

In the end, we have four appendices. \Cref{appA} depicts an improved
approximation for the second order susceptibility of the electrostatic
bremsstrahlung for Langmuir waves. In \Cref{appB} we discuss the
similarities of the asymptotic equilibrium state of the Langmuir waves
spectrum, considering a combination of an inverse power-law Kappa
distribution and a Maxwellian distribution, in the presence and the
absence of the electrostatic bremsstrahlung effect. The discussion in
\Cref{appB} is related to the article appended in \Cref{appC}, which
is parallel research and is only slightly connected to the main subject
of this work. \Cref{master} shows the paper that summarizes the results
of my Masters dissertation, which may be considered the starting point
of this doctoral research. % \Cref{appE} explores relevant aspects of
% current solar physics research and how they are connected to this work.
% It was written to be more like a light, informative reading, than a
% deep academic digression.

@@

The following paper\footnote{Credit: Reproduced from Physics of Plasmas 23,
  064504 (2016);\url{https://doi.org/10.1063/1.4953802}, with the permission
  of AIP Publishing.} is fairly self-sustained regarding the theory and methods
applied. All important equations are there, including their normalized form
and the normalization constants.

\includepdf[pages=2-6]{Tigik2016b.pdf}

\section{Generation of suprathermal electrons by collective processes
  in collisional plasmas}
\label{sec:gen-supr}
For the analysis of the electrostatic bremsstrahlung, the simple integration
of Eqs. \eqref{PkL} and \eqref{PkS}
was not very clarifying since we did not have any equivalent effect for
comparison. So we had to perform the time evolution of the system and analyze
the outcome. However, in order to put in evidence the action of the new effect,
is useful to start with the simplest possible situation. Therefore, instead of
using the complete set of nonlinear weak turbulence equations given by
Eqs. \eqref{L-gen} and \eqref{S-gen}, we restrict our analysis to the
quasilinear formalism, which includes single particle spontaneous emission
and wave-particle induced emission, and add the collisional damping and
electrostatic bremsstrahlung effects. The particle kinetic equation is
given by the usual quasilinear equation, where we included the Landau
collision integral (the same used in \cite{Tigik2016a}). After a long
evolution period, the system reaches a steady state where the electron
velocity distribution strongly resembles a core-halo distribution. An
interesting and surprising detail is that this suprathermal electron
population grows even in the presence of binary collisions. In the next
two subsections we provide some helpful information regarding the equations
and methods employed in \cite{Tigik2017a}.

@@

\subsection{Dimensionless equations}
In order to simplify the numerical analysis, it is convenient to write
the equations in terms of dimensionless variables. Thus, let us start
by some important definitions
\begin{align*}
  z\equiv \frac{\omega}{\omega_{pe}},
  & \quad \tau\equiv \omega_{pe}t, \quad
    {\bf q}\equiv \frac{{\bf k}v_e}{\omega_{pe}}, \quad
    {\bf u}\equiv \frac{\bf v}{v_e},\\
  \mu_{\bf q}^L
  = 1,&\quad\mu_{\bf q}^S = \frac{q^3}{2^{3/2}}
	\,\sqrt{\frac{m_e}{m_i}}\;\biggl(1+\frac{3T_i}{T_e}\biggr)^{1/2},\\
% \end{align*}
% \begin{align*}
  \Phi_a({\bf u})=  v_e^3 F_a({\bf u}),& \quad
    \calE_{\bf q}^{\sigma\alpha}= \frac{(2\pi)^2 g}{m_ev_e^2}
    \frac{I_{\bf k}^{\sigma\alpha}}{\mu_{\bf k}^\alpha},\quad
    P_{\bf k}^\alpha=\frac{m_ev_e^2}{(2\pi)^2g}\omega_{pe}P_{\bf q}^\alpha,\\
\end{align*}
where $g=1/[2^{3/2}\,(4\pi)^2\,\hat{n}\,\lambda_{De}^3]$ is the
plasma parameter, $\lambda_{De}=T_e/(4\pi\hat{n}e^2)=v_e^2/(2\omega_{pe}^2)$,
$v_e=(2T_e/m_e)^{1/2}$ is the electron thermal velocity and $T_e$ is the
electron temperature.

@@

The outcome of this analysis, along with a detailed discussion about
their importance in the context of solar and space physics can be seen
in the following paper\footnote{Credit: S. F. Tigik \emph{et al} 2017
  \emph{ApJL} {\bf 849} L30; \url{https://doi.org/10.3847/2041-8213/aa956f},
  reproduced by permission of the AAS.}.

@@

\chapter{Extra publication}
\label{appC}
This publication\footnote{Credit: Reproduced from Physics of Plasmas
  24, 112902 (2017);\url{https://doi.org/10.1063/1.5009931}, with the
  permission of AIP Publishing.} is mainly related with the results
presented in Ref.~\cite{Tigik2017a}. It can be said can say that most
of the ideas about the physical processes occurring in~\cite{Tigik2017a},
regarding the formation of the core-halo velocity distribution and the
fact that the electrostatic bremsstrahlung could be the underlying
process behind the ubiquity of such velocity distribution in the space
environment, came from the analysis of the results presented in
\cite{Tigik2017b}.

@@

\chapter{Two-dimensional time evolution of beam-plasma
  instability in the presence of binary collisions}
\label{master}
The paper\footnote{Credit: S. F. Tigik \emph{et al}, A\&A Volume 586,
  February 2016, \url{https://doi.org/10.1051/0004-6361/201527271},
  reproduced with permission, \textcopyright~ESO.} included in this
appendix is the complete text of Ref. \cite{Tigik2016a}, which
summarizes the outcomes of the Masters dissertation \cite{Tigik2015}
that led to the current doctoral research. This text was included
here with the intention to give the reader a complete view of the
work developed during my graduate studies.
